Synthesising Complex Termination Arguments

### 2014-06-03 papers/termination/kalashnikov.tex

\begin{tabular}{llll}
 \verb|add a b| & \verb|sub a b| & \verb|mul a b| & \verb|div a b| \\
 \verb|neg a| & & &
\end{tabular}

@@

\begin{tabular}{llll}
 \verb|and  a b| & \verb|or a b| & \verb|xor a b| & \verb|ashr a b| \\
 \verb|lshr a b| & \verb|not  a| & &
\end{tabular}

@@

\begin{tabular}{llll}
 \verb|le  a b| & \verb|lt  a b| & \verb|sle  a b| & \verb|slt a b|
\end{tabular}
\end{center}
}
 \caption{The language $\mathcal{L}$}
 \label{fig:l-language}
\end{figure}

@@

\resizebox{!}{2.3cm}{
\begin{tikzpicture}[font=\sffamily]

@@

The exact \newC encoding of an $\mathcal{L}$ program is shown in Fig.~\ref{fig:c-l-encoding}.
The \verb|prog_t| structure encodes a program, which is a sequence of instructions.
The parameter $a$ is the number of arguments the program takes.
The $i$th instruction has opcode \verb|ops[i]|, left operand \verb|params[i*2]| and
right operand \verb|params[i*2 + 1]|.  An operand refers to either a program constant,
a program argument or the result of a previous instruction, and its value
is determined at runtime as follows:
\[
 val(x) = \begin{cases}
           x < a & \text{the } x^{\text{th}} \text{ program argument} \\
           a \leq x < a+c & \mathtt{consts[} x-a \mathtt{]} \\
           x \geq a + c & \text{the result of the } (x - a - c)^{\text{th}} \text{ instruction}
          \end{cases}
\]

@@

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.7, transform shape, node distance=2cm, auto]
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

>>>>

\begin{tabular}{lll}
 \verb|add a b| & \verb|sub a b| & \verb|mul a b| \\
 \verb|neg a| & \verb|div a b|  & 
\end{tabular}

@@

\begin{tabular}{lll}
 \verb|and  a b| & \verb|or a b| & \verb|xor a b| \\
 \verb|lshr a b| & \verb|ashr a b| & \verb|not  a| 
\end{tabular}

@@

\begin{tabular}{lll}
 \verb|le  a b| & \verb|lt  a b| & \verb|sle  a b| \\
 \verb|slt a b| & &
\end{tabular}
\end{center}
}
 \caption{The language $\mathcal{L}$}
 \label{fig:l-language}
\end{figure}

@@

\resizebox{\linewidth}{!}{
\begin{tikzpicture}[font=\sffamily]

@@

The exact \newC encoding of an $\mathcal{L}$ program is shown in Fig.~\ref{fig:c-l-encoding}.
The \verb|prog_t| structure encodes a program, which is a sequence of instructions.
The parameter $a$ is the number of arguments the program takes.
The $i$th instruction has opcode \verb|ops[i]|, left operand \verb|params[i*2]| and
right operand \verb|params[i*2 + 1]|.  An operand refers to either a program constant,
a program argument or the result of a previous instruction, and its value
is determined at runtime as follows:
\[
 val(x) = \begin{cases}
           x < a & \text{the } x^{\text{th}} \text{ program argument} \\
           a \leq x < a+c & \mathtt{consts[} x-a \mathtt{]} \\
           x \geq a + c & \text{the result of instruction } (x - a - c)
          \end{cases}
\]

@@

\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.65, transform shape, node distance=2cm, auto]
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]
